\documentclass[10pt,a4paper]{article}

\usepackage[left=0.3in,right=0.3in,top=0.5in,bottom=0.5in,includehead, headheight=12pt, headsep=5pt]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{multirow}
% \usepackage{noto}
\usepackage{fancyhdr}
\usepackage{xcolor} % <-- REQUIRED FOR \textcolor

\usepackage{multicol} % <--- ADD THIS LINE HERE TO FIX THE ERROR

% % --- LATO FONT CONFIGURATION ---
% \usepackage[default]{lato} % Loads Lato as the default sans-serif font
% \usepackage[T1]{fontenc}    % Ensures clean font encoding and hyphenation
% % -------------------------------

% --- MULTI-FONT CONFIGURATION ---
\usepackage[T1]{fontenc}

% 1. Load Montserrat (For Main Headings)
\usepackage{montserrat}

% 2. Load Lato (For Project Titles/Subheadings)
% We remove [default] so it doesn't hijack the entire document
\usepackage[default]{lato} 

% 3. Load Nunito (Set as the Default Body Font)
% Nunito's package name is 'nunito'. The [default] option makes it the main text font.
% \usepackage[default]{nunito} 
% --------------------------------

\setstretch{0.95}
% \pagenumbering{gobble}
\pagestyle{fancy}

\fancyhf{} % Clear all default headers and footers

% Place page number in the top-right header
\rhead{\thepage}
\rhead{\raisebox{10pt}{\thepage\hspace{-5pt}}}
\rhead{\textcolor{black}{\thepage}}

% Define Footer Content
\lfoot{\color{black!50} Abhijit Karmakar}         % Left side: Name
\cfoot{\color{black!50} +91-9563828213}           % Center: Phone Number
\rfoot{\color{black!50} akarmakar846@gmail.com}   % Right side: Email Address
\setlength{\footskip}{25pt}                       % Adjust the distance of the footer

% Remove horizontal lines
\renewcommand{\headrulewidth}{0pt} % Removes top header line
\renewcommand{\footrulewidth}{0pt} % Removes bottom footer line
% Remove the default horizontal line under the header
\renewcommand{\headrulewidth}{0pt}

% \titlespacing*{command}{left-margin}{before-spacing}{after-spacing}
\titlespacing*{\section}{0pt}{4pt}{15pt}

\titleformat{\section}
%   {\fontfamily{Montserrat-LF}\selectfont\large\bfseries}
  {\large\bfseries}
  {}
  {0em}
  {}[\titlerule]

\title{Abhijit Karmakar}
\author{Abhijit}
\date{today}

\begin{document}
\thispagestyle{fancy} % <--- FORCE HEADER TO SHOW ON PAGE 1

%====================
% HEADER
%====================
\begin{center}
    {\LARGE \textbf{Abhijit Karmakar}} \\[4pt]
    Full-Stack Developer | Next.js | TypeScript | Node.js | PostgreSQL | SaaS | AI Automation | n8n | AWS \\[6pt]
    Gangarampur, West Bengal, India \\[4pt]
    \href{mailto:akarmakar846@gmail.com}{\color{blue}akarmakar846@gmail.com} \quad | \quad
    \href{tel:+919563828213}{\color{blue}+91 9563828213} \quad | \quad
    \href{https://www.linkedin.com/in/abhijit-karmakar}{\color{blue}Linkedin} \quad | \quad \href{https://github.com/abhijit47}{\color{blue}Github} \quad | \quad
    \href{https://www.abhijitdev.tech}{\color{blue}Website}
\end{center}

%====================
% SUMMARY
%====================
\section*{Professional Summary}
Full-Stack Developer with 3.5+ years of experience building scalable SaaS platforms, automation systems, and high-performance web applications using Next.js, TypeScript, Node.js, PostgreSQL, and MongoDB. Experienced in designing REST APIs, authentication systems, CI/CD pipelines, and cloud deployments. Delivered production-grade solutions across real estate, marketing automation, AI-powered applications, and agritech platforms. Passionate about leveraging technology to solve complex problems and drive business growth. Strong communicator and collaborator with a track record of working effectively in cross-functional teams.

%====================
% Core Competencies
%=====================
% \section*{Core Competencies}
% \vspace{-24pt}
% \begin{multicols}{2} % Splits the list into 2 equal columns
% \begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
%     \item SaaS Development
%     \item REST API Design
%     \item Authentication \& Authorization
%     \item Database Design
%     \item AI Integrations
%     \item Workflow Automation (n8n)
%     \item CI/CD
%     \item Cloud Deployment
%     \item Performance Optimization
% \end{itemize}
% \end{multicols}

%====================
% SKILLS
%====================
\section*{Technical Skills}
\vspace{-15pt}
\begin{tabular}{ |p{5cm}||p{13.5cm}|  }

 Category & Technologies\\
 \hline
 \textbf{Languages:}          & JavaScript, TypeScript, SQL\\
 \hline
 \textbf{Frontend:}           & React.js, Next.js, Redux, Tailwind CSS\\
 \hline
 \textbf{Backend:}            & Node.js, Express.js, REST APIs, tRPC\\
 \hline
 \textbf{Databases:}          & PostgreSQL, MongoDB, Redis\\
 \hline
 \textbf{DevOps:}             & Docker, GitHub Actions, CI/CD, Vercel\\
 \hline
 \textbf{Tools}               & n8n, Clerk, Stripe, Postman, Figma\\
 \hline
 \textbf{Cloud:}              & AWS (EC2, S3), GCP (Firebase)\\
 \hline
\end{tabular}

%====================
% EXPERIENCE
%====================
\section*{Professional Experience}
\vspace{-10pt}
\textbf{Leanitech} — Full-Stack Developer \hfill \textit{Feb 2023 – Present}  
Bengaluru, Karnataka, India  
\begin{itemize}[leftmargin=*, noitemsep]
    \item Delivered 40+ client projects across SaaS, real estate, healthcare, and e-commerce domains.
    \item Reduced average API latency from 500ms to 300ms through query optimization and indexing strategies.
    \item Designed multi-tenant SaaS architectures, scalable database schemas, and REST APIs for production applications.
    \item Implemented RBAC authentication supporting 5+ user roles and secure access controls.
    \item Built CI/CD pipelines using GitHub Actions and Vercel deployments.
    \item Integrated Stripe billing, Redis caching, and event-driven notification workflows.
\end{itemize}

\textbf{Stackkaroo} — MERN Stack Developer \hfill \textit{Dec 2022 – Mar 2023}  
Odisha, India  
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built responsive web applications using React.js, Next.js, and CSS with adaptive layouts across multiple screen sizes.
    \item Developed the company website and other sites using plain CSS and Material UI.
    \item Improved application performance and code reusability by implementing best practices and optimizing components, resulting in faster load times and enhanced user experience.
    \item Collaborated with cross-functional teams to gather requirements, design solutions, and deliver high-quality web applications that meet business needs and user expectations.
\end{itemize}

\textbf{TrueSkills} — Frontend Web Developer \hfill \textit{Aug 2022 – Nov 2022}  
Siliguri, West Bengal, India  
\begin{itemize}[leftmargin=*, noitemsep]
    \item Redesigned user interface to enhance user experience and engagement.
    \item Implemented responsive design principles for seamless functionality across devices.
    \item Used funnel builder tools to create visually appealing and conversion-focused landing pages.
    \item Collaborated with marketing team to optimize funnel performance and drive higher conversion rates.
\end{itemize}

%====================
% PROJECTS
%====================
\section*{Key Projects}
\vspace{-10pt}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Real Estate Management Platform:}  \hfill \textit{\href{https://github.com/abhijit47}{\color{blue}Preview}}
    \newline
    {\small \textbf{Technologies:} T3Stack, StreamIO, Novu, PostgreSQL, Arcjet, Cloudinary, Vercel}
    \begin{itemize}[leftmargin=*, noitemsep]
        \item Built real-time property exchange platform with integrated chat and notifications.
        \item Implemented StreamIO messaging and Novu notification services.
        \item Designed PostgreSQL schema and Cloudinary-based media management.
        \item Secured and deployed the platform using Arcjet and Vercel.
    \end{itemize}

    % {\small \textbf{Technologies:} Next.js, TypeScript, Node.js, PostgreSQL, Redis, StreamIO, Novu}
    % \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    % \end{itemize}
    
    \item \textbf{SaaS Bulk Email Marketing Tool:} \hfill \textit{\href{https://github.com/abhijit47}{\color{blue}Preview}}
    \newline
    {\small \textbf{Technologies:} Next.js, TypeScript, PostgreSQL, Drizzle ORM, Redis, Clerk}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
        \item Built multi-tenant email marketing platform supporting campaign creation and analytics.
        \item Implemented authentication using Clerk and role-based access control.
        \item Developed Redis-based email queue capable of processing thousands of emails asynchronously while preventing rate-limit issues.
        \item Designed PostgreSQL schema with Drizzle ORM for scalable data management.
    \end{itemize}

    \item \textbf{Comic Scene Generator:} \hfill \textit{\href{https://github.com/abhijit47}{\color{blue}Preview}}
    \newline
    {\small \textbf{Technologies:} Electron.js, Node.js, Midjourney AI, polling mechanism, Archiver.js}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
        \item Built desktop application using Electron.js for cross-platform compatibility.
        \item Integrated Midjourney AI for API-based image generation.
        \item Implemented polling mechanism to check for image generation status and retrieve results.
        \item Developed functionality to generate comic scenes and provide bulk zip downloads using Archiver.js.
    \end{itemize}

    % \item \textbf{Shimmer Plano Events:} \hfill \textit{\href{https://www.shimmerplanoevents.com}{\color{blue}Preview}}
    % \newline
    % {\small \textbf{Technologies:} Wordpress, Elementor, Other Wordpress Plugins}
    % \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    %     \item Designed and implemented a custom event management system to streamline the planning process for clients and the internal team.
    %     \item Implemented a user-friendly interface for event planning and management.
    %     \item Integrated contact forms and booking systems for seamless client communication.
    %     \item Optimized website performance and ensured mobile responsiveness for a wide audience reach.
    % \end{itemize}

    % \item \textbf{FinnoAQ:} \hfill \textit{\href{https://finnoaq.com}{\color{blue}Preview}}
    % \newline
    % {\small \textbf{Technologies:} Next.js, TypeScript, Bootstrap, Custom Theme, Web3 Form, Calendly}
    % \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    %     \item Developed a comprehensive website for FinnoAQ, showcasing their smart biofarm technology and sustainable farming solutions.
    %     \item Implemented a user-friendly interface to educate visitors about climate-smart farming practices and data-driven farming techniques.
    %     \item Integrated Web3 Form for secure and decentralized contact form submissions, enhancing user privacy and data security.
    %     \item Integrated Calendly for seamless scheduling of consultations and meetings with potential clients interested in sustainable farming solutions.
    % \end{itemize}

    % \item \textbf{Save Our Skies:} \hfill \textit{\href{https://github.com/abhijit47}{\color{blue}Preview}}
    % \newline
    % {\small \textbf{Technologies:} React, TypeScript, Tainwind CSS, Custom Design, Kaggle Dataset}
    % \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    %     \item Developed a visually appealing and user-friendly website for Save Our Skies, a student-led initiative supporting Raksha NGO in their mission to rescue and rehabilitate birds in need.
    %     \item Implemented a custom design using Tailwind CSS to create an engaging and informative platform that educates visitors about the critical work of Raksha NGO and encourages support for their cause.
    %     \item Integrated a Kaggle dataset to provide real-time information about bird rescue efforts, rehabilitation
    %     \item Implemented features to facilitate donations and volunteer sign-ups, helping to raise awareness and support for the initiative's mission to protect vulnerable bird species.
    % \end{itemize}

    \item \textbf{Chokhaa Store:} \hfill \textit{\href{https://chokhaa.com}{\color{blue}Preview}}
    \newline
    {\small \textbf{Technologies:} Shopify, Custom Theme Design, Custom Liquid Development, Razorpay Integration}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
        \item Developed custom Shopify storefront using Liquid and theme customization.
        \item Integrated Razorpay payments and product customization workflows.
        % \item Developed custom Liquid code to enhance the functionality of the Shopify platform, allowing for seamless product customization options and a smooth checkout process.
        % \item Integrated Razorpay payment gateway to provide secure and convenient payment options for customers, ensuring a seamless and trustworthy shopping experience on the website.
    \end{itemize}
\end{itemize}

\vspace{0pt}
\noindent
{\centering
\textit{See more projects:}  
\href{https://github.com/abhijit47?tab=repositories}{\color{blue}Github} | 
\href{https://www.linkedin.com/in/abhijit-karmakar/details/projects/}{\color{blue}Linkedin}\par}

% ====================
% Open Source
% ====================
\section*{Open Source Contributions}
\vspace{-10pt}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Devtools Blocker:} 
    % \newline
    % {\small \textbf{Technologies:} React.js, TypeScript, npm}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
        \item Built a React 18+ and TypeScript-compatible DevTools control hook to address compatibility limitations found in existing solutions.
        % \item Published and maintained the package with a focus on type safety, framework compatibility, and developer experience.
    \end{itemize}

    % {\small \textbf{Technologies:} Next.js, TypeScript, Node.js, PostgreSQL, Redis, StreamIO, Novu}
    % \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    %     \item Developed real-time property matching system.
    % \end{itemize}

    \item \textbf{React WhatsApp Widget:}
    % \newline
    % {\small \textbf{Technologies:} React.js, TypeScript, npm}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
        \item Built a Tailwind CSS and Shadcn/UI-friendly WhatsApp widget hook to solve customization and compatibility challenges found in legacy implementations.
    \end{itemize}


    \item \textbf{Rainbow color Generator:}
    % \newline
    % {\small \textbf{Technologies:} Typescript, npm}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Created a TypeScript-first color generation utility to modernize older implementations lacking strong typing and modern ecosystem compatibility.
    \end{itemize}
   
    \item \textbf{IFSC Code Validator:}
    % \newline
    % {\small \textbf{Technologies:} Typescript, npm}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Built a TypeScript-first IFSC validation utility using the official Razorpay bank dataset to improve reliability and modern ecosystem compatibility.
   \end{itemize}

    \item \textbf{EXIF Parser:}
    % \newline
    % {\small \textbf{Technologies:} Typescript, npm}
    \begin{itemize}[leftmargin=*, noitemsep, topsep=2pt]
    \item Modernized image metadata extraction with strong TypeScript support and simplified APIs for contemporary applications.
    \end{itemize}

%====================
% EDUCATION
%====================
\section*{Education}
\vspace{-10pt}
\textbf{Bachelor of Computer Applications (BCA)} \hfill \textit{Jun 2020 – Jul 2023} \newline
\small{Maulana Abul Kalam Azad University of Technology, West Bengal}
\newline
\small{CGPA: 9.05/10.0}

%====================
% CERTIFICATIONS
%====================
\section*{Certifications}
\vspace{-10pt}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \href{https://learn.mongodb.com/c/U2P6dWwiRzifJJPpkLv5vQ}{MongoDB Node.js Developer Path} \hfill \textit{Aug 2023}
    \item \href{https://verify.letsupgrade.in/certificate/LUEPAFSJUL123557}{Postman API Fundamental Student Expert} \hfill \textit{Aug 2023}
    \item \href{https://verify.letsupgrade.in/certificate/LUFS220162}{Fullstack Program in Web Development} \hfill \textit{Dec 2023}
\end{itemize}

\vspace{0pt}
\noindent
{\centering
\textit{See more details:}  
\href{https://www.linkedin.com/in/abhijit-karmakar/details/certifications/}
{\color{blue}Linkedin}\par}

% ====================
% INTERESTS
% ====================
% \section*{Interests}
% Exploring new technologies and frameworks, Contributing to open-source projects, Writing technical articles and tutorials, Traveling to new places and experiencing different cultures, Reading novels and literature for leisure and inspiration.

% ====================
% ACHIEVEMENTS
% ====================
\section*{Achievements}
\vspace{-10pt}
\begin{itemize}[leftmargin=*, noitemsep]
    % \item \textbf{Postman API Fundamentals Student Expert} - Earned the Postman API Fundamentals Student Expert certification, demonstrating proficiency in API testing and development.
    \item Delivered 40+ production client projects.
    \item Published 2 npm packages with 600+ combined downloads.
    % \item Built automation systems reducing manual workflow effort.
\end{itemize}

%====================
% LANGUAGES
%====================
\section*{Languages}
\vspace{-10pt}
English (Full Professional), Hindi (Full Professional), Bengali (Native)

\end{itemize}

%====================
% Signature
%====================
\vfill % Dynamically pushes everything below this line to the absolute bottom of the page

% \noindent
% \begin{flushright}
% \begin{minipage}{2.5in} % Constrains the signature block width
%     \centering
%     Abhijit Karmakar \\[6pt] % Extra space for physical/digital signature
%     \rule{2.5in}{0.4pt} \\ [4pt]    % Creates a clean horizontal signature line
%     \textbf{Date: \today} \hfill \tiny{Digital Signature} % Date on the right, with a note about digital signature
% \end{minipage}
% \end{flushright}

% \vspace{10pt} % Small gap between signature and disclosure
% \noindent
% {\scriptsize \color{black!60} \noindent
% \textit{\textbf{Privacy Notice:} The information provided in this curriculum vitae is shared strictly for employment consideration and professional evaluation purposes. Unauthorized distribution, commercial profiling, or third-party marketing use is not permitted.}}


\end{document}